A Comparative study of Dask and Spark for data-intensive neuroimaging pipelines

### 2019-07-11 latex/paper.tex
Worked on BidsApp example restuls section

Figure~\ref{fig:inc_gantt} shows the Gantt chart obtained for each engine and API,
for a baseline execution with 125 blocks, a \SI{4}{\second} sleep delay and 8
workers. Gantt charts are structured in batches of up to 64 read-compute-write
concurrent sequences. File reads in the first batch are much longer than in the
following ones: this is due to the high synchronization of data transfers that leads
to a high saturation of the shared file system. We also note that overhead,
represented in white, is concentrated around the data transfer tasks \TG{find out
why}, and the computing tasks that run concurrently with data transfers. 
% The frameworks have similar makespan however the time spend for each type of
% task differs considerably (see Table~\ref{tab:inc_base}). Spark tends to spend more
% time than other frameworks for IO however it has a much lower overhead. Dask Delayed
% and Futures have the lowest IO time but a much higher overhead. Dask Bag stands in
% the middle for both IO and overhead. Compute time is approximately the same for all
% frameworks. Apart from the first IO section, there is a large amount of ovehead
% everytime time IO is performed. This is true for all frameworks.

\begin{figure*}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/spark_inc_gantt.png}
        \caption{Spark}\label{fig:inc_spark_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/bag_inc_gantt.png}%
        \caption{Dask Bag}\label{fig:inc_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/delayed_inc_gantt.png}%
        \caption{Dask Delayed}\label{fig:inc_dask_delayed_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/futures_inc_gantt.png}%
        \caption{Dask Futures}\label{fig:inc_dask_futures_gantt}
    \end{subfigure}
    \caption{Gantt chart with 125 blocks, \SI{4}{\second} delay, 8 workers}\label{fig:inc_gantt}
\end{figure*}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_worker.png}%
        \caption{Histogram makespan}\label{fig:histo_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_worker.png}%
        \caption{Histogram total time}\label{fig:histo_tt_worker}
    \end{subfigure}
    \caption{125 blocks}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_block.png}%
        \caption{Histogram makespan}\label{fig:histo_ms_block}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_block.png}%
        \caption{Histogram total time}\label{fig:histo_tt_block}
    \end{subfigure}
    \caption{8 workers}
\end{figure}
\TG{We decided to omit Dask Futures as it does not have any value over Dask
Delayed in this application.}

%%% BIDS EXAMPLE %%%
\subsection{BidsApp example: Number of workers}

@@

%% Baseline gantt chart
\subsection{BidsApp example: Gantt chart}

% Figure~\ref{fig:inc_gantt} shows the Gantt chart obtained for each engine and API,
% for a baseline execution with 125 blocks, a \SI{4}{\second} sleep delay and 8
% workers. Gantt charts are structured in batches of up to 64 read-compute-write
% concurrent sequences. File reads in the first batch are much longer than in the
% following ones: this is due to the high synchronization of data transfers that leads
% to a high saturation of the shared file system. We also note that overhead,
% represented in white, is concentrated around the data transfer tasks \TG{find out
% why}, and the computing tasks that run concurrently with data transfers. 
% The frameworks have similar makespan however the time spend for each type of
% task differs considerably (see Table~\ref{tab:inc_base}). Spark tends to spend more
% time than other frameworks for IO however it has a much lower overhead. Dask Delayed
% and Futures have the lowest IO time but a much higher overhead. Dask Bag stands in
% the middle for both IO and overhead. Compute time is approximately the same for all
% frameworks. Apart from the first IO section, there is a large amount of ovehead
% everytime time IO is performed. This is true for all frameworks.

@@

Mathieu Dugr\'e was funded by a Undergraduate Summer Research Assistant
award from the National Science and Engineering Research Council. We warmly
thank Compute Canada and \TG{Westgrid?} for providing the cloud
infrastructure used in these experiments, and the McGill Center for
Integrative Neurocience for giving us access to their cloud allocation.

>>>>

Figure~\ref{fig:inc_gantt} shows the Gantt chart obtained for each engine and API.
Gantt charts are structured in batches of up to 64 read-compute-write concurrent
sequences. File reads in the first batch are much longer than in the following ones:
this is due to the high synchronization of data transfers that leads to a high
saturation of the shared file system. We also note that overhead, represented in
white, is concentrated around the data transfer tasks \TG{find out why}, and the
computing tasks that run concurrently with data transfers. 
% The frameworks have similar makespan however the time spend for each type of
% task differs considerably (see Table~\ref{tab:inc_base}). Spark tends to spend more
% time than other frameworks for IO however it has a much lower overhead. Dask Delayed
% and Futures have the lowest IO time but a much higher overhead. Dask Bag stands in
% the middle for both IO and overhead. Compute time is approximately the same for all
% frameworks. Apart from the first IO section, there is a large amount of ovehead
% everytime time IO is performed. This is true for all frameworks.

\begin{figure*}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/spark_inc_gantt.png}
        \caption{Spark}\label{fig:inc_spark_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/bag_inc_gantt.png}%
        \caption{Dask Bag}\label{fig:inc_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/delayed_inc_gantt.png}%
        \caption{Dask Delayed}\label{fig:inc_dask_delayed_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/futures_inc_gantt.png}%
        \caption{Dask Futures}\label{fig:inc_dask_futures_gantt}
    \end{subfigure}
    \caption{Gantt chart with 125 blocks, 10 iterations, \SI{4}{\second} delay, 8
    workers, 8 threads/worker}\label{fig:inc_gantt}
\end{figure*}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_worker.png}%
        \caption{Histogram makespan}\label{fig:histo_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_worker.png}%
        \caption{Histogram total time}\label{fig:histo_tt_worker}
    \end{subfigure}
    \caption{125 blocks, 8 threads/worker}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_block.png}%
        \caption{Histogram makespan}\label{fig:histo_ms_block}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_block.png}%
        \caption{Histogram total time}\label{fig:histo_tt_block}
    \end{subfigure}
    \caption{8 workers, 8 threads/worker}
\end{figure}
\TG{We decided to omit Dask Futures as it does not have any value over Dask
Delayed in this application.}

%%% BIDS EXAMPLE %%%
\subsection{BidsApp example: Number of workers}
Figure~\ref{fig:bids_ms_worker} shows the makespan of the application while varying
the amount of worker. Overall, there is no substantial difference between the
engines however Futures are always slightly faster. The performance difference between
Futures and the other APIs increase with the number of workers. The makespan scales
well with the increase in workers however the scaling reduces considerably when
reaching 8 workers. This due to the IO requirement increasing with the number of
workers, since more tasks are read concurrently, and the application becomes more data
intensive.

In Figure~\ref{fig:bids_tt_worker}, the total execution time of each function is
shown. \MD{Maybe mention why Spark overhead is so big.} Overall, the computation time
for the group analysis is equal for all engines and numbers of workers. Bag and
Delayed takes much longer to compute the participant analysis with 8 workers,
otherwise, the makespan is similar for all engines and numbers of workers. The overhead
increases as the number of workers increases. \MD{Check regression}

\MD{Depending on how the overhead is calculated spark overhead is either minimal or
gigantic. It is hard to determine which method should be used to calculate the
overhead for this application. For this application, since Spark has 2 job this
causes Spark to have different worker process for the different job and thus some job
have overlaping process ID while other are uniques (See
Figure~\ref{fig:bids_spark_gantt}).}

@@

%% Baseline gantt chart
\subsection{BidsApp example: Gantt chart}
Figure~\ref{fig:bids_gantt} shows the Gantt charts obtained for each engine and API.
The Gantt charts are structured in three main parts: participant analysis (orange),
group analysis (blue), and the transition in between.\MD{rephrase} The Gantt chart
for Spark seems to have more workers however it does not. This is due to the
computation of the participant and group analysis on two different jobs with their
worker processes; usually with different process id. The tasks differ considerably in
length. This is due to the high IO requirement of the application. During the
participant analysis phase, Spark and Futures have less overhead than Delayed and
Bag. At the end of the participant analysis phase, Futures and Delayed has less
overhead than Bag while Spark has way more than Dask engine. The group analysis is
similar for all engines and APIs.

@@

Mathieu Dugr\'e was funded by a Undergraduate Student Research Assistant award from
the National Science and Engineering Research Council of Canada. We warmly thank
Compute Canada and \TG{Westgrid?} for providing the cloud infrastructure used in
these experiments, and the McGill Center for Integrative Neurocience for giving us
access to their cloud allocation.
